Supplementary Materials- A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-03-02 analysis/paper/supplementary-material.Rmd
revised the SI and the table in it

-  further historical background of 17th century northeastern Taiwan in a pericolonial context
-  further review of network analysis and archaeological applications
-  further definition of our approach to tie formation and node attributes from Kiwulan burials
-  further details on methods of modeling fitting, and
-  assessment of MCMC output and Goodness-of-fit diagnostics for our models

@@

```{r age-sex-table}
library(flextable)
age_sex_by_phase <-
  burial_three_period_age_tidy %>% 
  select(Age_scale, gender, Phase) %>% 
  group_by(Phase, gender, Age_scale) %>% 
  filter(!Phase %in% c("disturbed", "chi")) %>% 
  count() %>% 
  pivot_wider(names_from = c(Phase, gender), 
              values_from = n) %>% 
  mutate(Age_scale = factor(Age_scale,
                            levels = c("0-12", "12-20", "+20", "NA"))) %>% 
  arrange(Age_scale) %>% 
  rename(age = Age_scale) %>% 
  select(age, pre_male, pre_female, pre_NA, post_male, post_female, post_NA)

ft_age_sex <- flextable(age_sex_by_phase) %>% 
  set_header_labels(pre_male = "pre-European", pre_female = "pre-European",
                    pre_NA = "pre-European", post_male = "post-European", 
                    post_female ="post-European", post_NA = "post-European") %>%
  merge_at(i = 1, j = 2:4, part = "header") %>% 
  merge_at(i = 1, j = 5:7, part = "header") %>% 
  add_header_row(values = c("","male", "female", "NA", 
                            "male", "female", "NA"), top = FALSE) %>% 
  align(j = 2:7, align = "right", part = "header") %>% 
  align(i = 1, align = "center", part = "header") %>% 
  set_caption("The number of burials with identification of age and sex at Kiwulan. The NA means no sufficient skeletal remains for determination of age or sex")
ft_age_sex
```

>>>>

-  further historical background of 17th century northeastern Taiwan in a pericolonial context
-  further review of network analysis and archaeological applications relevant to this study
-  further definitions of our approach to tie formation and node attributes from Kiwulan burials
-  further details on our methods of modeling fitting, and
-  assessment of our MCMC output and Goodness-of-fit diagnostics for our models

@@

```{r age-sex-table}
library(flextable)
age_sex_by_phase <-
  burial_three_period_age_tidy %>% 
  select(Age_scale, gender, Phase) %>% 
  group_by(Phase, gender, Age_scale) %>% 
  filter(!Phase %in% c("disturbed", "chi")) %>% 
  count() %>% 
  pivot_wider(names_from = c(Phase, gender), 
              values_from = n) %>% 
  rename(age = Age_scale) %>% 
  mutate(age = ifelse(age == "NA", "unknown", age)) %>% 
  mutate(age = factor(age,
                      levels = c("0-12", "12-20", "+20", "unknown"))) %>% 
  arrange(age) %>% 
  select(age, pre_male, pre_female, pre_NA, post_male, post_female, post_NA) %>% 
  mutate_all(., funs(replace_na(., 0)))

ft_age_sex <- flextable(age_sex_by_phase) %>% 
  colformat_double(digits = 0) %>%
  set_header_labels(pre_male = "pre-European", pre_female = "pre-European",
                    pre_NA = "pre-European", post_male = "post-European", 
                    post_female ="post-European", post_NA = "post-European") %>%
  merge_at(i = 1, j = 2:4, part = "header") %>% 
  merge_at(i = 1, j = 5:7, part = "header") %>% 
  add_header_row(values = c("","male", "female", "unknown", 
                            "male", "female", "unknown"), top = FALSE) %>% 
  align(j = 2:7, align = "right", part = "header") %>% 
  align(i = 1, align = "center", part = "header") %>% 
  set_caption("The number of burials with identification of age and sex at Kiwulan. The NA means no sufficient skeletal remains for determination of age or sex")
ft_age_sex
```
